Qeury-Driven Central Slot-Values Extraction for Wikipedia Entities at Web Scale

### 2013-11-03 paper/flairs27/content/abstract.tex

In this paper we will present the system design and algorithm adopted by the 
GatorDSR team, University of Florida to efficiently process TREC KBA 2013 --- 
SSF track. Here we will describe the system as well as the details 
the algorithms used to extract slot values for the given slot name. Scalability, efficiency, precision and recall are the major goals of this work, 
given the overly limited time limitation and available computational resources.

>>>>

In this paper we address extracting central slot values from internet pertinent to entities in wikipedia, which is the most popular web-based, colaborative multilingual encyclopieda on the internet. This is comparable to Freebase in a query-driven manner. Our contributions are two fold, first we design a system to efficiently find central documents on the internet that contain directly citable information regarding a given wikipedia entity; second, we design a system to extract specific features of that entity from central documents which is refered to as slot filling. Our results demonstrate that the system is very efficient in the web scale nature of the problem: being highly memory and I/O efficient and that we can achieve high accuracy and recall for given slot values.

### 2013-11-03 paper/flairs27/content/appendix.tex
Updating paper independent of trek kba terminology

\subsection{Streaming Slot Filling (SSF)}
The task is that given certain WP or Twitter entities 
(wiki/twitter URLs) and certain relations of interest (given in
Table~\ref{table:slotNameOntology}), extract as many triple relations as possible (
hence, slot filling). This can be used to automatically populate knowledgebases 
such as free-base or DBPedia or even fill-in the information boxes at Wikipedia. 
Below, you can view some examples of what it means to fill in a slot value; in 
each example there is a sentence of interest that we wish to extract slot values 
from, an entity that the slot value is related to, and a slot name which can be 
thought of as the topic of the slot value:

@@

\begin{table}[h]
\caption{Ontology of Slot Name Categories }
\centering
\label{table:slotNameOntology}

>>>>

\subsection{Streaming Slot Filling (SSF)}
The task is that given certain WP or Twitter entities (wiki/twitter URLs) and certain relations of interest (given in Table~\ref{table:slotNameOntology}), extract as many triple relations as possible (hence, slot filling). This can be used to automatically populate knowledgebases such as free-base or DBPedia or even fill-in the information boxes at Wikipedia. Below, you can view some examples of what it means to fill in a slot value; in each example there is a sentence of interest that we wish to extract slot values from, an entity that the slot value is related to, and a slot name which can be thought of as the topic of the slot value:

@@

\begin{table}[T]
\caption{Ontology of Slot Name Categories }
\centering
\label{table:slotNameOntology}

### 2013-11-03 paper/flairs27/content/discussion.tex
remove extra newlines instead of wrap

\section{Discussion \& Future Works}

@@

When we evaluate the results of slot extraction, we find 
three kinds of problems for accuracy: 1) wrong entities found; 2) wrong tags 
by the Lingpipe; 3) wrong results matched by the patterns.  We also have 
recall problems: 1) not enough good alias names to find all the entities. 2) 
not enough and powerful patterns to capture all the slot values.

We will use entity resolution methods and other advanced methods to improve 
the accuracy and recall of entity extraction part.

@@

>>>>

\section{Discussions \& Conclusion}

@@

When we evaluate the results of slot extraction, we find three kinds of problems for accuracy: 1) wrong entities found; 2) wrong tags by the Lingpipe; 3) wrong results matched by the patterns.  We also have 
recall problems: 1) not enough good alias names to find all the entities. 2) not enough and powerful patterns to capture all the slot values. We will use entity resolution methods and other advanced methods to improve 
the accuracy and recall of entity extraction part.

@@

Alltogether, We experimented through different tools and approaches to best process the massive amounts of data on the platform that we had available to us. We generate aliases for wikipedia entities using Wiki API and extract some aliases from wikipedia pages text itself. On twitter entities we extract aliases manually as it is part of the rule of the KBA track. We process documents that mention entities for slot value extraction. Slot values are determined using pattern matching over coreferences of entities in sentences. Finally post processing will filter, cleanup and infers some new slot values to enhance recall and accuracy.

We noticed that some tools that claim to be performant for using the hardware capabilities at hand sometimes don't really work as claimed and you should not always rely on one without a thorough A/B testing of performance which we ended up in generating our in-house system for processing the corpus and generating the index. Furthermore, on extracting slot values, pattern matching might not be the best options but definitely can produce some good results at hand. We have plans on generating classifiers for slot value extraction 
purposes. Entity resolution on the other hand was a topic we spent sometime on but could not get to stable grounds for it. Entity resolution will distinguish between entities of the same name but different contexts. Further improvements on this component of the system are required.

### 2013-11-03 paper/flairs27/content/implementation.tex

We use Wikipedia API to get some aliases automatically. This is done by retrieving backlink references (redirects of a wiki entity). Unfortunately this is not good enough and to enhance recall we need more aliases. To have better use of a wiki page we parse HTML DOM of the page, then use regular expressions to extract the bold phrases of the first paragraph as alias of the actual entity. Based on our observation this is a very accurate heuristic and provides us with lots of famous aliases of the entities. To consider other 
typical cases we consider some generic first name last name order swapping conventions such as Bill Gates $\rightarrow$ Gates, Bill.  Meanwhile, William Henry Gates is an alias for Bill Gates in WP as a backlink reference. These kinds of aliases are also included in matching entities.

@@

Our pipeline of processing the corpus consists of a two layer indexing system referred to as \textit{Chunk Files Index Generator} and \textit{StreamItems Index Generator}. Chunk Files Index Generator will generate indexes of the chunk files that contain a mention of any of the desired entities. StreamItems Index Generator 
on the other hand will index StreamItems that contain a mention of a given entity respectively. This two level indexing will eliminate the need to process each and every ChunkFile/StreamItem for every entity. The reason for splitting this task into two steps is that not all chunk files contain any mention of the entities and 
we want to get rid of them as soon as possible. Chunk Files Index Generator which is written in C++ discards non-mentioning chunk files and will stop further processing a chunk file as soon as it finds a mention there. Each chunk file can contain up to thousands of SIs which can be so time consuming if we were to process them in our Java base code. Processing StreamItems on the other hand is done in Java with ideas in mind for later on extensibility by adding other Java libraries.

@@

In the data set, we are given 4 months of data (October 2011 - February 2012) as training data. Instead of building a classifier we use pattern matching methods to find corresponding slot values for entities. 
Pattern matching is simple to manipulate results and implement. Additionally, a classifier approach is more difficult to evaluate and explain results.

With the Streamitem indexes generated by the CCR, we first fetch the sentences containing entites by using alias names and coreference information provided by Lingpipe tags. Then use these senteces to match patterns and when patterns matched, generate SSF results.

>>>>

We consider some generic first name last name order swapping conventions such as Bill Gates $\rightarrow$ Gates, Bill.  Meanwhile, William Henry Gates is an alias for Bill Gates in WP as a backlink reference. These kinds of aliases are also included in matching entities. We use Wikipedia API to get these aliases automatically. This is done by retrieving backlink references (redirects of a wiki entity). Unfortunately this is not good enough and to enhance recall we need more aliases. To have better use of a wiki page we parse HTML DOM of the page, then use regular expressions to extract the bold phrases of the first paragraph as alias of the actual entity. Based on our observation this is a very accurate heuristic and provides us with lots of famous aliases of the entities. As an example of when this might not wirk, is that there might be occasions that some other topic is written in bold typesetting in the first paraph apart from the entity aliases itself but these are very rare

@@

Our pipeline of processing the corpus consists of a two layer indexing system referred to as \textit{Chunk Files Index Generator} and \textit{StreamItems Index Generator}. Chunk Files Index Generator will generate indexes of the chunk files that contain a mention of any of the desired entities. StreamItems Index Generator 
on the other hand will index StreamItems that contain a mention of a given entity respectively. This two level indexing will eliminate the need to process each and every ChunkFile/StreamItem for every entity. The reason for splitting this task into two steps is that not all chunk files contain any mention of the entities and 
we want to get rid of them as soon as possible. Chunk Files Index Generator which discards non-mentioning chunk files and will stop further processing a chunk file as soon as it finds a mention there. Each chunk file can contain up to thousands of SIs which can be so time consuming if we were to process them in our Java base code. Processing StreamItems on the other hand is done in Java with ideas in mind for later on extensibility by adding other Java libraries.

@@

In the data set, we are given a date range of documents as training data. Instead of building a classifier we use pattern matching methods to find corresponding slot values for entities. 
Pattern matching is simple to manipulate results and implement. Additionally, a classifier approach is more difficult to evaluate and explain results.

With the StreamItem indexes generated by the CCR, we first fetch the sentences containing entites by using alias names and coreference information provided by Lingpipe tags. Then use these senteces to match patterns and when patterns matched, generate SSF results.

### 2013-11-03 paper/flairs27/content/introduction.tex

In this paper, we describe the system we built to process the data. We built this system as part of a formal task described in Section~\ref{sec:kbatask}. Our approach to this task is to build a modular system
that allows us to explore the nuances of the training data and queries. Overall, we contribute the following:
\begin{itemize}[noitemsep,nolistsep]
\item Introduce a method to build models of name variations (Section \ref{section:aliasgeneration});
\item Built a system to filter a large amount of diverse documents (Section~\ref{sec:ccrimpl});
\item Extract entity-slot-value triples of information to be added to KB (Section~\ref{sec:ssve});
\item Filter the final results using deduplication and inference (Section~\ref{section:highAccuracyFilter});
\item Self-evaluate our results over a 4.5 TB data set (Section\ref{sec:results}).
\end{itemize}

>>>>

In this paper, we describe the system we built to process the data. We built this system as part of a formal task described in Section~\ref{sec:kbatask}. Our approach to this task is to build a modular system
that allows us to explore the nuances of the training data and queries. Overall, we contribute the following:
\begin{itemize}[noitemsep,nolistsep]
\item Introduce a method to build models of name variations %(Section \ref{section:aliasgeneration});
\item Built a system to filter a large amount of diverse documents %(Section~\ref{sec:ccrimpl});
\item Extract entity-slot-value triples of information to be added to KB %(Section~\ref{sec:ssve});
\item Filter the final results using deduplication and inference %(Section~\ref{section:highAccuracyFilter});
\item Self-evaluate our results over a 4.5 TB data set %(Section\ref{sec:results}).
\end{itemize}
